Arrows for Parallel Computations

### 2017-05-18 paper/content/main.tex
this is how inline works with lhs2tex

\newcommand{\inlinecode}[1]{\texttt{#1}}

@@

\olcomment{Parrows + accelerate = love? Metion port to Frege. Mention the Par monad troubles.}
	%\pagebreak
        \bibliographystyle{jfp}
	\bibliography{references,main}
        \appendix
	\section{Utility Functions}\label{utilfns}
To be able to go into detail on parallel arrows, we introduce some utility combinators first, that will help us later: \inlinecode{map}, \inlinecode{foldl} and \inlinecode{zipWith} on arrows.

The \inlinecode{mapArr} combinator (Fig.~\ref{fig:mapArr}) lifts any arrow \inlinecode{arr a b} to an arrow \inlinecode{arr [a] [b]} \cite{programming_with_arrows}:

@@

\caption{\inlinecode{map} over arrows}

@@

Similarly, we can also define \inlinecode{foldlArr} (Fig.~\ref{fig:foldlArr}) that lifts any arrow \inlinecode{arr (b, a) b} with a neutral element \inlinecode{b} to \inlinecode{arr [a] b}:

@@

\caption{\inlinecode{foldl} over arrows}

@@

Finally, with the help of \inlinecode{mapArr} (Fig.~\ref{fig:mapArr}), we can define \inlinecode{zipWithArr} (Fig.~\ref{fig:zipWithArr}) that lifts any arrow \inlinecode{arr (a, b) c} to an arrow \inlinecode{arr ([a], [b]) [c]}.

@@

\caption{\inlinecode{zipWith} over arrows}

@@

These combinators make use of the \inlinecode{ArrowChoice} type class which provides the \pipepipepipe\olcomment{CHECK!} combinator. It takes two arrows \inlinecode{arr a c} and \inlinecode{arr b c} and combines them into a new arrow \inlinecode{arr (Either a b) c} which pipes all \inlinecode{Left a}'s to the first arrow and all \inlinecode{Right b}'s to the second arrow.

@@

With the zipWithArr combinator we can also write a combinator \inlinecode{listApp} (Fig.~\ref{fig:listApp}), that lifts a list of arrows \inlinecode{[arr a b]} to an arrow \inlinecode{arr [a] [b]}.
\begin{figure}[h]
\begin{hscode}\SaveRestoreHook
\column{B}{@{}>{\hspre}l<{\hspost}@{}}%
\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
\>[B]{}\Varid{listApp}\mathbin{::}(\Conid{ArrowChoice}\;\Varid{arr},\Conid{ArrowApply}\;\Varid{arr})\Rightarrow [\mskip1.5mu \Varid{arr}\;\Varid{a}\;\Varid{b}\mskip1.5mu]\to \Varid{arr}\;[\mskip1.5mu \Varid{a}\mskip1.5mu]\;[\mskip1.5mu \Varid{b}\mskip1.5mu]{}\<[E]%
\\
\>[B]{}\Varid{listApp}\;\Varid{fs}\mathrel{=}(\Varid{arr}\mathbin{\$}\lambda \Varid{as}\to (\Varid{fs},\Varid{as}))\mathbin{>\!\!>\!\!>}\Varid{zipWithArr}\;\Varid{app}{}\<[E]%
\ColumnHook
\end{hscode}\resethooks
\caption{Definition of \inlinecode{listApp}}
\label{fig:listApp}
\end{figure}
% $ %% formatting
. Note that  this additionally makes use of the \inlinecode{ArrowApply} typeclass that allows us to evaluate arrows with \inlinecode{app :: arr (arr a b, a) c}.

>>>>

%\newcommand{\inlinecode}[1]{\texttt{#1}}
\newcommand{\inlinecode}[1]{\emph{#1}} %%% booo
%%% |code| is inline code in lhs2tex

@@

\olcomment{Parrows + accelerate = love? Metion port to Frege. Mention the Par monad troubles.}
	%\pagebreak
        \bibliographystyle{jfp}
	\bibliography{references,main}
        \appendix
	\section{Utility Functions}\label{utilfns}
To be able to go into detail on parallel arrows, we introduce some utility combinators first, that will help us later: \ensuremath{\Varid{map}}, \ensuremath{\Varid{foldl}} and \ensuremath{\Varid{zipWith}} on arrows.

The \ensuremath{\Varid{mapArr}} combinator (Fig.~\ref{fig:mapArr}) lifts any arrow \ensuremath{\Varid{arr}\;\Varid{a}\;\Varid{b}} to an arrow \ensuremath{\Varid{arr}\;[\mskip1.5mu \Varid{a}\mskip1.5mu]\;[\mskip1.5mu \Varid{b}\mskip1.5mu]} \cite{programming_with_arrows}:

@@

\caption{\ensuremath{\Varid{map}} over arrows}

@@

Similarly, we can also define \ensuremath{\Varid{foldlArr}} (Fig.~\ref{fig:foldlArr}) that lifts any arrow \ensuremath{\Varid{arr}\;(\Varid{b},\Varid{a})\;\Varid{b}} with a neutral element \ensuremath{\Varid{b}} to \ensuremath{\Varid{arr}\;[\mskip1.5mu \Varid{a}\mskip1.5mu]\;\Varid{b}}:

@@

\caption{\ensuremath{\Varid{foldl}} over arrows}

@@

Finally, with the help of \ensuremath{\Varid{mapArr}} (Fig.~\ref{fig:mapArr}), we can define \ensuremath{\Varid{zipWithArr}} (Fig.~\ref{fig:zipWithArr}) that lifts any arrow \ensuremath{\Varid{arr}\;(\Varid{a},\Varid{b})\;\Varid{c}} to an arrow \ensuremath{\Varid{arr}\;([\mskip1.5mu \Varid{a}\mskip1.5mu],[\mskip1.5mu \Varid{b}\mskip1.5mu])\;[\mskip1.5mu \Varid{c}\mskip1.5mu]}.

@@

\caption{\ensuremath{\Varid{zipWith}} over arrows}

@@

These combinators make use of the \ensuremath{\Conid{ArrowChoice}} type class which provides the \pipepipepipe\olcomment{CHECK!} combinator. It takes two arrows \ensuremath{\Varid{arr}\;\Varid{a}\;\Varid{c}} and \ensuremath{\Varid{arr}\;\Varid{b}\;\Varid{c}} and combines them into a new arrow \ensuremath{\Varid{arr}\;(\Conid{Either}\;\Varid{a}\;\Varid{b})\;\Varid{c}} which pipes all \ensuremath{\Conid{Left}\;\Varid{a}}'s to the first arrow and all \ensuremath{\Conid{Right}\;\Varid{b}}'s to the second arrow.

@@

With the zipWithArr combinator we can also write a combinator \ensuremath{\Varid{listApp}} (Fig.~\ref{fig:listApp}), that lifts a list of arrows \ensuremath{[\mskip1.5mu \Varid{arr}\;\Varid{a}\;\Varid{b}\mskip1.5mu]} to an arrow \ensuremath{\Varid{arr}\;[\mskip1.5mu \Varid{a}\mskip1.5mu]\;[\mskip1.5mu \Varid{b}\mskip1.5mu]}.
\begin{figure}[h]
\begin{hscode}\SaveRestoreHook
\column{B}{@{}>{\hspre}l<{\hspost}@{}}%
\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
\>[B]{}\Varid{listApp}\mathbin{::}(\Conid{ArrowChoice}\;\Varid{arr},\Conid{ArrowApply}\;\Varid{arr})\Rightarrow [\mskip1.5mu \Varid{arr}\;\Varid{a}\;\Varid{b}\mskip1.5mu]\to \Varid{arr}\;[\mskip1.5mu \Varid{a}\mskip1.5mu]\;[\mskip1.5mu \Varid{b}\mskip1.5mu]{}\<[E]%
\\
\>[B]{}\Varid{listApp}\;\Varid{fs}\mathrel{=}(\Varid{arr}\mathbin{\$}\lambda \Varid{as}\to (\Varid{fs},\Varid{as}))\mathbin{>\!\!>\!\!>}\Varid{zipWithArr}\;\Varid{app}{}\<[E]%
\ColumnHook
\end{hscode}\resethooks
\caption{Definition of \ensuremath{\Varid{listApp}}}
\label{fig:listApp}
\end{figure}
% $ %% formatting
. Note that  this additionally makes use of the \ensuremath{\Conid{ArrowApply}} typeclass that allows us to evaluate arrows with \ensuremath{\Varid{app}\mathbin{::}\Varid{arr}\;(\Varid{arr}\;\Varid{a}\;\Varid{b},\Varid{a})\;\Varid{c}}.
